Hydrodynamics of a Semipermeable Inextensible Membrane Under Flow and Confinement

### 2021-05-20 vesicle_code/docs/permeableVes/Response2Refs.tex
yny5

>>>>

    It is true that in some cases the two-dimensional vesicle hydrodynamics may have very little inference to the corresponding three-dimensional vesicle hydrodynamics. We have undertaken the full three-dimensional simulation of a semipermeable vesicle going through strong confinement, where the three-dimensional effects may be important.
